---
title: "Range1: Mean+/- 2SD 16.89) - 1D/2D/3D"
output: html_notebook
---
### This protocol requires slice numbers of anatomical landmarks (from step 1, code: 1_sliceselection.imj) to locate the body regions.

```{r}
install.packages("oro.nifti")
install.packages("oro.dicom")

library(oro.dicom)
library(rlist)
library(oro.nifti)
```

################ INPUTS FROM IMAGEJ ###########################
```{r}
slice_number_start_rabbit <- 12  # put the slice number of the most cranial part of cranial extremity (for whole body count)
slice_number_end_rabbit <- 638 # put the slice number of the most cranial part of cranial extremity (for whole body count)
slice_number_start_abdomen <- 206  # put the slice number of liver
slice_number_end_abdomen <-400 # put the slice number of the femoral head
rescale_intercept <- -8192 # Put interception to rescale the image intensities before counting
```

############ SLICE POSITIONE FOR KIDNEYS ###############
```{r}
right_kidney<- 2
left_kidney<- 258
```

###### HU range 1: for this rabbit (FWHM +/- 2SD) = -116.75 +/- 16.98 ######
```{r}
HU_value_adipose_at_max_freq =-116.75 #From imagej specific for rabbit
HU_value_adipose_offset_at_half_max_freq = 16.98 #From ImageJ value is specific for each rabbit
```


### ################ END OF INPUTS FROM IMAGEJ##############
```{r}
####### Setting up results dataFrame(S) for 1D, 2D and 3D analysis
df_results_1D <- data.frame(matrix(vector(),ncol=5))
colnames(df_results_1D) <-c("animal_ID", "wholeBody_1D","abdomen_1D","r_kidney_1D", "l_kidney_1D")

df_results_2D <- data.frame(matrix(vector(),ncol=5)) # dataframe for counts  allowing for nearest neighbor in the slice
colnames(df_results_2D) <-c("animal_ID", "wholeBody_2D","abdomen_2D","r_kidney_2D", "l_kidney_2D")

df_results_3D <- data.frame(matrix(vector(),ncol=5)) # dataframe for counts  allowing for nearest neighbor in the slice and in immediate neighbor slices
colnames(df_results_3D) <-c("animal_ID", "wholeBody_3D","abdomen_3D","r_kidney_3D", "l_kidney_3D")
```

### Image Directory ###

```{r}
## put image directory
dicom_path <- "C:\\Users\\dlf490\\OneDrive - University of Copenhagen\\Desktop\\RABBIT_CT\\Rabbit_DEXA image\\DEXA_XRAY\\DEXA29_M94578\\CT"

dcmImages <- readDICOM(dicom_path, verbose = TRUE, recursive = TRUE)

patientID <- extractHeader(dcmImages$hdr[1], string="PatientID", numeric=FALSE)

dim(t(dcmImages$img))
```


```{r}
range1_max = HU_value_adipose_at_max_freq + HU_value_adipose_offset_at_half_max_freq 

range1_min = HU_value_adipose_at_max_freq - HU_value_adipose_offset_at_half_max_freq

range1_max
range1_min
```


### #############################################################
### #############################################################


### ############## KIDNEY #####################
### ############## KIDNEY #####################
### ############## KIDNEY #####################

### ############## ONE SLICE - left kidney 1D #####################
```{r}
im_data <- t(dcmImages$img[[left_kidney]])
D1_mask_im_data <- t(dcmImages$img[[left_kidney]])
D1_mask_im_data[,]<-0

im_data_HU <- im_data + rescale_intercept
r1_l_kidney = length(which(im_data_HU>=range1_min & im_data_HU <= range1_max))
#print(length(which(im_data_HU>=range1_min & im_data_HU <= range1_max)))

counter=0
for (i in 1:512){
  for (j in 1:512){
    if (im_data_HU[i,j]>= range1_min & im_data_HU[i,j]<= range1_max){
      counter= counter+1
      D1_mask_im_data[i,j] <- 7200
      #print(im_data_HU[i,j])
    }
  }
}
counter

image(im_data, col = grey(0:64/64), axes = FALSE, xlab = "left kidney", ylab = "", useRaster = TRUE)
image(D1_mask_im_data, col = grey(0:64/64), axes = FALSE, xlab = "left kidney D1 mask", ylab = "", useRaster = TRUE)
 
##SAVE TO RESULTS
df_results_1D[1,"animal_ID"]= patientID
df_results_1D[1,"l_kidney_1D"]=r1_l_kidney
df_results_1D[1, "HU_min"] <- range1_min
df_results_1D[1, "HU_max"] <- range1_max
df_results_1D


############################################################
# Automatically use the same directory as the DICOM images
output_dir <- dicom_path  # Use the same path as readDICOM()

# Add patientID as prefix to the filenames
nifti_image_filename <- paste0(patientID, "_left_kidney_R1_1D_image")
nifti_mask_filename <- paste0(patientID, "_left_kidney_R1_1D_mask")

# Save the NIfTI files with the updated filenames
writeNIfTI(im_data, file.path(output_dir, nifti_image_filename))
writeNIfTI(D1_mask_im_data, file.path(output_dir, nifti_mask_filename))

cat("NIfTI files saved in:", output_dir, "\n")

```

### ############## ONE SLICE - right kidney 1D #####################
```{r}
im_data <- t(dcmImages$img[[right_kidney]])
D1_mask_im_data <- t(dcmImages$img[[right_kidney]])
D1_mask_im_data[,]<-0

im_data_HU <- im_data + rescale_intercept
pixel_counter = length(which(im_data_HU>=range1_min & im_data_HU <= range1_max))
#print(length(which(im_data_HU>=range1_min & im_data_HU <= range1_max)))


for (i in 1:512){
  for (j in 1:512){
    if (im_data_HU[i,j]>= range1_min & im_data_HU[i,j]<= range1_max){
      D1_mask_im_data[i,j] <- 7200
      #print(im_data_HU[i,j])
    }
  }
}

image(im_data, col = grey(0:64/64), axes = FALSE, xlab = "right kidney", ylab = "", useRaster = TRUE)
image(D1_mask_im_data, col = grey(0:64/64), axes = FALSE, xlab = "right kidney D1 mask", ylab = "", useRaster = TRUE)

##SAVE TO RESULTS
df_results_1D[1,"animal_ID"]= patientID
df_results_1D[1,"r_kidney_1D"]=pixel_counter
df_results_1D


############################################################
# Automatically use the same directory as the DICOM images
output_dir <- dicom_path  # Use the same path as readDICOM()

# Add patientID as prefix to the filenames
nifti_image_filename <- paste0(patientID, "_right_kidney_R1_1D_image")
nifti_mask_filename <- paste0(patientID, "_right_kidney_R1_1D_mask")

# Save the NIfTI files with the updated filenames
writeNIfTI(im_data, file.path(output_dir, nifti_image_filename))
writeNIfTI(D1_mask_im_data, file.path(output_dir, nifti_mask_filename))

cat("NIfTI files saved in:", output_dir, "\n")


```

### ############## ONE SLICE - left kidney 2D #####################
```{r}
pixel_counter <- 0
im_data <- t(dcmImages$img[[left_kidney]])
D2_mask_im_data <- t(dcmImages$img[[left_kidney]])
D2_mask_im_data[100,100]
D2_mask_im_data[,]<-0
#D2_mask_im_data[100,100]

im_data_HU <- im_data + rescale_intercept
for (i in 2:511){
  for (j in 2:511){
    cube = list(im_data_HU[i-1,j-1],im_data_HU[i-1,j],im_data_HU[i-1,j+1],
                im_data_HU[i,j-1],im_data_HU[i,j],im_data_HU[i,j+1],
                im_data_HU[i+1,j-1],im_data_HU[i+1,j],im_data_HU[i+1,j+1]
                )
    if (sum(cube>=range1_min & cube <=range1_max)==9){
        pixel_counter <-  pixel_counter+1
        D2_mask_im_data[i,j] <- 7200
    }
  }
}

pixel_counter


image(im_data, col = grey(0:64/64), axes = FALSE, xlab = "left kidney", ylab = "", useRaster = TRUE)
image(D2_mask_im_data, col = grey(0:64/64), axes = FALSE, xlab = "left kidney D2 mask", ylab = "", useRaster = TRUE)
df_results_2D[1,"l_kidney_2D"] <- pixel_counter
df_results_2D[1,"animal_ID"]= patientID
df_results_2D[1, "HU_min"] <- range1_min
df_results_2D[1, "HU_max"] <- range1_max
df_results_2D


############################################################
# Automatically use the same directory as the DICOM images
output_dir <- dicom_path  # Use the same path as readDICOM()

# Add patientID as prefix to the filenames
nifti_image_filename <- paste0(patientID, "_left_kidney_R1_2D_image")
nifti_mask_filename <- paste0(patientID, "_left_kidney_R1_2D_mask")

# Save the NIfTI files with the updated filenames
writeNIfTI(im_data, file.path(output_dir, nifti_image_filename))
writeNIfTI(D2_mask_im_data, file.path(output_dir, nifti_mask_filename))

cat("NIfTI files saved in:", output_dir, "\n")
 
```

### ############## ONE SLICE - right kidney 2D #####################
```{r}
pixel_counter <- 0
im_data <- t(dcmImages$img[[right_kidney]])
D2_mask_im_data <- t(dcmImages$img[[right_kidney]])
D2_mask_im_data[100,100]
D2_mask_im_data[,]<-0
#D2_mask_im_data[100,100]

im_data_HU <- im_data + rescale_intercept
for (i in 2:511){
  for (j in 2:511){
    cube = list(im_data_HU[i-1,j-1],im_data_HU[i-1,j],im_data_HU[i-1,j+1],
                im_data_HU[i,j-1],im_data_HU[i,j],im_data_HU[i,j+1],
                im_data_HU[i+1,j-1],im_data_HU[i+1,j],im_data_HU[i+1,j+1]
    )
    if (sum(cube>=range1_min & cube <=range1_max)==9){
      pixel_counter <-  pixel_counter+1
      D2_mask_im_data[i,j] <- 7200
    }
  }
}

pixel_counter


image(im_data, col = grey(0:64/64), axes = FALSE, xlab = "Right Kidney", ylab = "", useRaster = TRUE)
image(D2_mask_im_data, col = grey(0:64/64), axes = FALSE, xlab = "right ridney D2 mask", ylab = "", useRaster = TRUE)


df_results_2D[1,"animal_ID"]= patientID
df_results_2D[1, "r_kidney_2D"] <- pixel_counter
df_results_2D[1, "HU_min"] <- range1_min
df_results_2D[1, "HU_max"] <- range1_max
df_results_2D


############################################################
# Automatically use the same directory as the DICOM images
output_dir <- dicom_path  # Use the same path as readDICOM()

# Add patientID as prefix to the filenames
nifti_image_filename <- paste0(patientID, "_right_kidney_R1_2D_image")
nifti_mask_filename <- paste0(patientID, "_right_kidney_R1_2D_mask")

# Save the NIfTI files with the updated filenames
writeNIfTI(im_data, file.path(output_dir, nifti_image_filename))
writeNIfTI(D2_mask_im_data, file.path(output_dir, nifti_mask_filename))

cat("NIfTI files saved in:", output_dir, "\n")


```

### ############# One Slice - left kidney 3D #######################
```{r}
pixel_counter=0
slice_number=left_kidney
im_data <- t(dcmImages$img[[slice_number]])
im_data_less_one <- t(dcmImages$img[[slice_number-1]])
im_data_plus_one <- t(dcmImages$img[[slice_number+1]])
D3_mask_im_data <- t(dcmImages$img[[slice_number]])
D3_mask_im_data[100,100]
D3_mask_im_data[,]<-0
D3_mask_im_data[100,100]


im_data_HU <- im_data + rescale_intercept
im_data_HU_less_one <- im_data_less_one + rescale_intercept
im_data_HU_plus_one <- im_data_plus_one + rescale_intercept
for (i in 2:511){
  for (j in 2:511){
    cube = list(im_data_HU[i-1,j-1],im_data_HU[i-1,j],im_data_HU[i-1,j+1],
                im_data_HU[i,j-1],im_data_HU[i,j],im_data_HU[i,j+1],
                im_data_HU[i+1,j-1],im_data_HU[i+1,j],im_data_HU[i+1,j+1],
                im_data_HU_less_one[i-1,j-1],im_data_HU_less_one[i-1,j],im_data_HU_less_one[i-1,j+1],
                im_data_HU_less_one[i,j-1],im_data_HU_less_one[i,j],im_data_HU_less_one[i,j+1],
                im_data_HU_less_one[i+1,j-1],im_data_HU_less_one[i+1,j],im_data_HU_less_one[i+1,j+1],
                im_data_HU_plus_one[i-1,j-1],im_data_HU_plus_one[i-1,j],im_data_HU_plus_one[i-1,j+1],
                im_data_HU_plus_one[i,j-1],im_data_HU_plus_one[i,j],im_data_HU_plus_one[i,j+1],
                im_data_HU_plus_one[i+1,j-1],im_data_HU_plus_one[i+1,j],im_data_HU_plus_one[i+1,j+1]
                )
    if (sum(cube>=range1_min & cube <=range1_max)==27){
      pixel_counter <-  pixel_counter+1
      D3_mask_im_data[i,j] <- 7200
    }
  }
}

pixel_counter


image(im_data, col = grey(0:64/64), axes = FALSE, xlab = "left kidney", ylab = "", useRaster = TRUE)
image(D3_mask_im_data, col = grey(0:64/64), axes = FALSE, xlab = "left kidney D3 mask", ylab = "", useRaster = TRUE)


df_results_3D[1,"animal_ID"]= patientID
df_results_3D[1, "l_kidney_3D"] <- pixel_counter
df_results_3D[1, "HU_min"] <- range1_min
df_results_3D[1, "HU_max"] <- range1_max
df_results_3D


# Automatically use the same directory as the DICOM images
output_dir <- dicom_path  # Use the same path as readDICOM()

# Add patientID as prefix to the filenames
nifti_image_filename <- paste0(patientID, "_left_kidney_R1_3D_image")
nifti_mask_filename <- paste0(patientID, "_left_kidney_R1_3D_mask")

# Save the NIfTI files with the updated filenames
writeNIfTI(im_data, file.path(output_dir, nifti_image_filename))
writeNIfTI(D3_mask_im_data, file.path(output_dir, nifti_mask_filename))

cat("NIfTI files saved in:", output_dir, "\n")
```


### ############# One Slice - right kidney 3D #######################
```{r}
pixel_counter=0
slice_number=right_kidney
im_data <- t(dcmImages$img[[slice_number]])
im_data_less_one <- t(dcmImages$img[[slice_number-1]])
im_data_plus_one <- t(dcmImages$img[[slice_number+1]])
D3_mask_im_data <- t(dcmImages$img[[slice_number]])
D3_mask_im_data[100,100]
D3_mask_im_data[,]<-0
D3_mask_im_data[100,100]


im_data_HU <- im_data + rescale_intercept
im_data_HU_less_one <- im_data_less_one + rescale_intercept
im_data_HU_plus_one <- im_data_plus_one + rescale_intercept
for (i in 2:511){
  for (j in 2:511){
    cube = list(im_data_HU[i-1,j-1],im_data_HU[i-1,j],im_data_HU[i-1,j+1],
                im_data_HU[i,j-1],im_data_HU[i,j],im_data_HU[i,j+1],
                im_data_HU[i+1,j-1],im_data_HU[i+1,j],im_data_HU[i+1,j+1],
                im_data_HU_less_one[i-1,j-1],im_data_HU_less_one[i-1,j],im_data_HU_less_one[i-1,j+1],
                im_data_HU_less_one[i,j-1],im_data_HU_less_one[i,j],im_data_HU_less_one[i,j+1],
                im_data_HU_less_one[i+1,j-1],im_data_HU_less_one[i+1,j],im_data_HU_less_one[i+1,j+1],
                im_data_HU_plus_one[i-1,j-1],im_data_HU_plus_one[i-1,j],im_data_HU_plus_one[i-1,j+1],
                im_data_HU_plus_one[i,j-1],im_data_HU_plus_one[i,j],im_data_HU_plus_one[i,j+1],
                im_data_HU_plus_one[i+1,j-1],im_data_HU_plus_one[i+1,j],im_data_HU_plus_one[i+1,j+1]
    )
    if (sum(cube>=range1_min & cube <=range1_max)==27){
      pixel_counter <-  pixel_counter+1
      D3_mask_im_data[i,j] <- 7200
    }
  }
}

pixel_counter


image(im_data, col = grey(0:64/64), axes = FALSE, xlab = "right kidney", ylab = "", useRaster = TRUE)
image(D3_mask_im_data, col = grey(0:64/64), axes = FALSE, xlab = "right kidney D3 mask", ylab = "", useRaster = TRUE)

df_results_3D[1,"animal_ID"]= patientID
df_results_3D[1, "r_kidney_3D"] <- pixel_counter
df_results_3D[1, "HU_min"] <- range1_min
df_results_3D[1, "HU_max"] <- range1_max
df_results_3D

# Automatically use the same directory as the DICOM images
output_dir <- dicom_path  # Use the same path as readDICOM()

# Add patientID as prefix to the filenames
nifti_image_filename <- paste0(patientID, "_right_kidney_R1_3D_image")
nifti_mask_filename <- paste0(patientID, "_right_kidney_R1_3D_mask")

# Save the NIfTI files with the updated filenames
writeNIfTI(im_data, file.path(output_dir, nifti_image_filename))
writeNIfTI(D3_mask_im_data, file.path(output_dir, nifti_mask_filename))

cat("NIfTI files saved in:", output_dir, "\n")
```


### ############## W H O L E   B O D Y ########################
### ############## W H O L E   B O D Y ########################
### ############## W H O L E   B O D Y ########################

### ################ WHOLE BODY - 1D #################
```{r}
pixel_counter <- 0 # A COUNTER OF PIXELS WHOS VALES ARE IN "RANGE 1"
for (i in (slice_number_start_rabbit+1):slice_number_end_rabbit-1){
  im_data <- t(dcmImages$img[[i]])
  im_data_HU <- im_data + rescale_intercept
  pixel_counter = pixel_counter+length(which(im_data_HU>=range1_min & im_data_HU <= range1_max))
}

pixel_counter
# HU range 1  for all slices
##SAVE TO RESULTS
df_results_1D[1,"animal_ID"]= patientID
df_results_1D[1,"wholeBody_1D"]=pixel_counter
df_results_1D

```

### ################ WHOLE BODY - 2D #################
```{r}
pixel_counter <- 0 # A COUNTER OF PIXELS WHOS VALES ARE IN "RANGE 1"
for (h in (slice_number_start_rabbit+1):slice_number_end_rabbit-1){
  im_data <- t(dcmImages$img[[h]])
  im_data_HU <- im_data + rescale_intercept
  
  for (i in 2:511){
    for (j in 2:511){
    cube = list(im_data_HU[i-1,j-1],im_data_HU[i-1,j],im_data_HU[i-1,j+1],
                im_data_HU[i,j-1],im_data_HU[i,j],im_data_HU[i,j+1],
                im_data_HU[i+1,j-1],im_data_HU[i+1,j],im_data_HU[i+1,j+1]
                )
      if (sum(cube>=range1_min & cube <=range1_max)==9){
      pixel_counter <-  pixel_counter+1
    }
  }

  }
  print(h)
}

pixel_counter
# HU range 1  for all slices
##SAVE TO RESULTS
df_results_2D[1,"animal_ID"]= patientID
df_results_2D[1,"wholeBody_2D"]=pixel_counter
df_results_2D

```

### ################# WHOLE BODY - 3D #################
```{r}
pixel_counter <- 0 # A COUNTER OF PIXELS WHOS VALES ARE IN "RANGE 1"
for (h in (slice_number_start_rabbit+1):(slice_number_end_rabbit-1)){
  im_data <- t(dcmImages$img[[h]])
  im_data_less_one <- t(dcmImages$img[[h-1]])
  im_data_plus_one <- t(dcmImages$img[[h+1]])
  im_data_HU <- im_data + rescale_intercept
  im_data_HU_less_one <- im_data_less_one + rescale_intercept
  im_data_HU_plus_one <- im_data_plus_one + rescale_intercept
  
  for (i in 2:511){
    for (j in 2:511){
      cube = list(im_data_HU[i-1,j-1],im_data_HU[i-1,j],im_data_HU[i-1,j+1],
                im_data_HU[i,j-1],im_data_HU[i,j],im_data_HU[i,j+1],
                im_data_HU[i+1,j-1],im_data_HU[i+1,j],im_data_HU[i+1,j+1],
                im_data_HU_less_one[i-1,j-1],im_data_HU_less_one[i-1,j],im_data_HU_less_one[i-1,j+1],
                im_data_HU_less_one[i,j-1],im_data_HU_less_one[i,j],im_data_HU_less_one[i,j+1],
                im_data_HU_less_one[i+1,j-1],im_data_HU_less_one[i+1,j],im_data_HU_less_one[i+1,j+1],
                im_data_HU_plus_one[i-1,j-1],im_data_HU_plus_one[i-1,j],im_data_HU_plus_one[i-1,j+1],
                im_data_HU_plus_one[i,j-1],im_data_HU_plus_one[i,j],im_data_HU_plus_one[i,j+1],
                im_data_HU_plus_one[i+1,j-1],im_data_HU_plus_one[i+1,j],im_data_HU_plus_one[i+1,j+1]
    )
      if (sum(cube>=range1_min & cube <=range1_max)==27){
        pixel_counter <-  pixel_counter+1
      }
    }
  }
  print(h)
}

pixel_counter
# HU range 1  for all slices
##SAVE TO RESULTS
df_results_3D[1,"animal_ID"]= patientID
df_results_3D[1,"wholeBody_3D"]=pixel_counter
df_results_3D
```
```{r}
slice_number_start_rabbit
slice_number_end_rabbit
```


### ################# A B D O M EN #########################
### ################# A B D O M EN #########################
### ################# A B D O M EN #########################

### ############### ABDOMEN - 1D ##############################
```{r}
pixel_counter <- 0 # A COUNTER OF PIXELS WHOS VALES ARE IN "RANGE 1"
for (i in (slice_number_start_abdomen):slice_number_end_abdomen){
  im_data <- t(dcmImages$img[[i]])
  im_data_HU <- im_data + rescale_intercept
  pixel_counter = pixel_counter+length(which(im_data_HU>=range1_min & im_data_HU <= range1_max))
}

pixel_counter
# HU range 1  for all slices
##SAVE TO RESULTS
df_results_1D[1,"animal_ID"]= patientID
df_results_1D[1,"abdomen_1D"]=pixel_counter
df_results_1D
```

### ############## ABDOMEN - 2D ################
```{r}
pixel_counter <- 0 # A COUNTER OF PIXELS WHOS VALES ARE IN "RANGE 1"
for (h in (slice_number_start_abdomen):slice_number_end_abdomen){
  im_data <- t(dcmImages$img[[h]])
  im_data_HU <- im_data + rescale_intercept
  
  for (i in 2:511){
    for (j in 2:511){
      cube = list(im_data_HU[i-1,j-1],im_data_HU[i-1,j],im_data_HU[i-1,j+1],
                  im_data_HU[i,j-1],im_data_HU[i,j],im_data_HU[i,j+1],
                  im_data_HU[i+1,j-1],im_data_HU[i+1,j],im_data_HU[i+1,j+1]
      )
      if (sum(cube>=range1_min & cube <=range1_max)==9){
        pixel_counter <-  pixel_counter+1
      }
    }
    
  }
  print(h)
}

pixel_counter
# HU range 1  for all slices
##SAVE TO RESULTS
df_results_2D[1,"animal_ID"]= patientID
df_results_2D[1,"abdomen_2D"]=pixel_counter
df_results_2D

```

### ################ ABDOMEN - 3D ################
```{r}
pixel_counter <- 0 # A COUNTER OF PIXELS WHOS VALES ARE IN "RANGE 1"
for (h in (slice_number_start_abdomen):slice_number_end_abdomen){
  im_data <- t(dcmImages$img[[h]])
  im_data_less_one <- t(dcmImages$img[[h-1]])
  im_data_plus_one <- t(dcmImages$img[[h+1]])
  im_data_HU <- im_data + rescale_intercept
  im_data_HU_less_one <- im_data_less_one + rescale_intercept
  im_data_HU_plus_one <- im_data_plus_one + rescale_intercept
  
  for (i in 2:511){
    for (j in 2:511){
      cube = list(im_data_HU[i-1,j-1],im_data_HU[i-1,j],im_data_HU[i-1,j+1],
                im_data_HU[i,j-1],im_data_HU[i,j],im_data_HU[i,j+1],
                im_data_HU[i+1,j-1],im_data_HU[i+1,j],im_data_HU[i+1,j+1],
                im_data_HU_less_one[i-1,j-1],im_data_HU_less_one[i-1,j],im_data_HU_less_one[i-1,j+1],
                im_data_HU_less_one[i,j-1],im_data_HU_less_one[i,j],im_data_HU_less_one[i,j+1],
                im_data_HU_less_one[i+1,j-1],im_data_HU_less_one[i+1,j],im_data_HU_less_one[i+1,j+1],
                im_data_HU_plus_one[i-1,j-1],im_data_HU_plus_one[i-1,j],im_data_HU_plus_one[i-1,j+1],
                im_data_HU_plus_one[i,j-1],im_data_HU_plus_one[i,j],im_data_HU_plus_one[i,j+1],
                im_data_HU_plus_one[i+1,j-1],im_data_HU_plus_one[i+1,j],im_data_HU_plus_one[i+1,j+1]
    )
      if (sum(cube>=range1_min & cube <=range1_max)==27){
        pixel_counter <-  pixel_counter+1
        
      }
    }
  }
  print(h)
}

pixel_counter
# HU range 1  for all slices
##SAVE TO RESULTS
df_results_3D[1,"animal_ID"]= patientID
df_results_3D[1,"abdomen_3D"]=pixel_counter
df_results_3D
```


### #################### LAST STEP ######################
### #################### LAST STEP ######################

#### Exports the 3 dataframes to csv files
```{r}
df_results_1D
df_results_2D
df_results_3D

write.csv(df_results_1D,paste0(dicom_path, patientID,"_R1_1Dn.csv"), row.names = FALSE)
write.csv(df_results_2D,paste0(dicom_path, patientID,"_R1_2Dn.csv"), row.names = FALSE)
write.csv(df_results_3D,paste0(dicom_path, patientID,"_R1_3Dn.csv"), row.names = FALSE)


dicom_path

print("completed !")
```


### #################### E N D ######################
### #################### E N D ######################

